A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-10-01 journal/experiments.tex
typo fix

To our knowledge, the state-of-the-art in research on advancing fuzzing triage over the tools built into fuzzers like AFL is represented by the \emph{semantic crash bucketing} (SCB) approach of van Tonder, Kotheimer, and Le Goues \cite{SCB}.  This approach uses patch templates based on common types of bugs/semi-fixes, combined with semantic information obtained by observing the execution of a crashing input, to bucket crashing inputs discovered by fuzzers.  We contacted the SCB authors, and with their cooperation investigated how well SCB handled the fuzzgoat crashes.  The fuzzgoat code highlights the primary limitation of SCB: namely, if a kind of failure is not handled by a (manually constructed) patch template and identified by the semantic feedback mechanisms, then SCB does not really handle it.  The SCB tool was able to produce a patch for one of the four fuzzgoat bugs, a null pointer dereference.  Unfortunately, at present, SCB does not handle bugs related to misuse of {\tt free} (use-after-free, double frees, or frees of invalid pointers), and the other three fuzzgoat bugs are all {\tt free}-related.  SCB therefore can very effectively identify the inputs associated with one of the four bugs (when it is the only one triggeered by the input), but provides no assistance with finding the other three bugs. This is not to say that SCB is useless here; the null pointer bug is responsible for 15 of the 38 crashes, so SCB does make it easy to see an instance of the null pointer bug, and ignore 14 additional inputs.  It does not, however, help find the rare bug with only a few instances among the remaining 23 inputs.  While mutation repair also has no knowledge of {\tt free} bugs, it is able to find mutants that avoid their symptoms or their causes, and thus triage all four faults effectively.   The SCB team added the fuzzgoat example to their published VM, and plan to use it to drive development of patch templates and analysis for use-after-frees; this will, at some point, likely make it possible for SCB to handle fuzzgoat effectively.  However, in the long term, if fuzzing is applied to find assertion violations, differential testing divergences \cite{Differential,ICSEDiff}, or other more complex ``custom'' properties, as is likely with the appearance of tools such as DeepState \cite{DeepState} that merge fuzzing and property-based testing, it is hard to see how SCB will handle these ``custom'' bug types.

@@

Unsurprisingly, the repairing-mutants approach does not improve on SCB on the set of bugs from the SCB paper \cite{SCB}.  These bugs were intentionally selected to consist of null pointers and buffer overflows; SCB in this setting operates as a bucketing version of repair that only has to use a selected, known-relevant set of mutants.  Repair is good at ranking the crashes for these subjects, but unable to provide bucketing, and more difficult to set up and more expensive (though still relatively cheap---it requires minutes for taming, vs. the seconds of SCB) than SCB.  When SCB applies, it is likely to be faster and more useful than mutant-based FPF ranking.  However, a user will obviously seldom know for certain that all faults in a set of crashes correlate to bug types that SCB supports. One approach would be to use SCB to bucket crashes, and then apply our approach to any remaining inputs, and examine the first few inputs in repair-FPF order.  In Section \ref{conc} we will return to this point.

>>>>

To our knowledge, the state-of-the-art in research on advancing fuzzing triage over the tools built into fuzzers like AFL is represented by the \emph{semantic crash bucketing} (SCB) approach of van Tonder, Kotheimer, and Le Goues \cite{SCB}.  This approach uses patch templates based on common types of bugs/semi-fixes, combined with semantic information obtained by observing the execution of a crashing input, to bucket crashing inputs discovered by fuzzers.  We contacted the SCB authors, and with their cooperation investigated how well SCB handled the fuzzgoat crashes.  The fuzzgoat code highlights the primary limitation of SCB: namely, if a kind of failure is not handled by a (manually constructed) patch template and identified by the semantic feedback mechanisms, then SCB does not really handle it.  The SCB tool was able to produce a patch for one of the four fuzzgoat bugs, a null pointer dereference.  Unfortunately, at present, SCB does not handle bugs related to misuse of {\tt free} (use-after-free, double frees, or frees of invalid pointers), and the other three fuzzgoat bugs are all {\tt free}-related.  SCB therefore can very effectively identify the inputs associated with one of the four bugs, but provides no assistance with finding the other three bugs. This is not to say that SCB is useless here; the null pointer bug is responsible for 15 of the 38 crashes, so SCB does make it easy to see an instance of the null pointer bug, and ignore 14 additional inputs.  It does not, however, help find the rare bug with only a few instances among the remaining 23 inputs.  While mutation repair also has no knowledge of {\tt free} bugs, it is able to find mutants that avoid their symptoms or their causes, and thus triage all four faults effectively.   The SCB team added the fuzzgoat example to their published VM, and plan to use it to drive development of patch templates and analysis for use-after-frees; this will, at some point, likely make it possible for SCB to handle fuzzgoat effectively.  However, in the long term, if fuzzing is applied to find assertion violations, differential testing divergences \cite{Differential,ICSEDiff}, or other more complex ``custom'' properties, as is likely with the appearance of tools such as DeepState \cite{DeepState} that merge fuzzing and property-based testing, it is hard to see how SCB will handle these ``custom'' bug types.

@@

Unsurprisingly, the repairing-mutants approach does not improve on SCB on the set of bugs from the SCB paper \cite{SCB}.  These bugs were intentionally selected to consist of null pointers and buffer overflows; SCB in this setting operates as a bucketing version of repair that only has to use a selected, known-relevant set of mutants.  Repair is good at ranking the crashes for these subjects, but unable to provide bucketing, and more difficult to set up and more expensive (though still relatively cheap --- it requires minutes for taming, vs. the seconds of SCB) than SCB.  When SCB applies, it is likely to be faster and more useful than mutant-based FPF ranking.  However, a user will obviously seldom know for certain that all faults in a set of crashes correlate to bug types that SCB supports. One approach would be to use SCB to bucket crashes, and then apply our approach to any remaining inputs, and examine the first few inputs in repair-FPF order.  In Section \ref{conc} we will return to this point.
